legacy effects

### 2018-12-27 analysis/legacy_effects.Rmd
add legacy effects

---
title: "legacy effects"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
editor_options: 
  chunk_output_type: console
---

@@

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
library("here")
library("pander")
library("rms")
library("magrittr")
library("lemon")
```

@@

@@

p1 <- mlegacy %>% ggplot(aes(x = ypd, y = mean)) + 
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill=site), alpha=.5) + 
  geom_line(aes(colour=site)) + 
  geom_point(aes(colour=site), size=3) + 
  geom_line(data = l2005, aes(x = ypd, y =  lag)) + 
  geom_line(data = l2012, aes(x = ypd, y =  lag), linetype = "dashed") + 
  facet_wrap(~site, labeller = as_labeller(label_site)) + 
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'black') + 
  theme(panel.grid = element_blank(), 
        strip.background = element_blank(), 
        legend.position = "none") + 
  scale_x_continuous("Years post drougth event", breaks=c(1:6)) + 
  scale_y_continuous("Observed - Predicted Growth", breaks=seq(-0.4, 0.2, by=0.05))

>>>>

---
title: "legacy effects"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: gfm
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

@@

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
library("here")
library("pander")
# library("rms")
library("magrittr")
library("lemon")
```

@@

## Legacy effects for all Q. pyrenaica forests

```{r}
all_legacy <- legacy %>% group_by(ypd) %>%
  summarise(mean=mean(lag, na.rm=T),
            sd = sd(lag, na.rm=T),
            se = sd/sqrt(length(lag)))

po <- position_dodge(0.9)
all_legacy %>% 
  ggplot(aes(x = ypd, y = mean)) + 
  geom_line(position = po, alpha=0.8) + 
  geom_point(position = po) + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), position = po) +
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'black') + 
  theme(panel.grid = element_blank()) + 
  scale_x_continuous("Years post drougth event", breaks=c(1:6)) + 
  scale_y_continuous("Observed - Predicted Growth")

# Boostrap Confidence Intervals 
set.seed(1234)

all_legacy_nest <- legacy %>% 
  group_by(ypd) %>% 
  nest()

all_legacy_nest %<>% 
  dplyr::mutate(booted = purrr::map(.x = data, # The list-column containing <S3: tibble>
                                      ~ boot::boot(data = .x$lag, # The <S3 tibble> column being sampled
                                                 statistic = boot_mean, # The user-defined function
                                                 R = 10000, # The number of replicates
                                                 stype = "i")))

# compute the Confidence interval 
all_legacy_nest %<>%
    dplyr::mutate(booted_ci = purrr::map(.x = booted, # The list-column containing <S3: boot> objects
                                         ~ boot::boot.ci(.x,
                                                         conf = 0.95, # Interval width
                                                         type = "bca")))  # Calculate a BCa interval
# Tidy the CI 
all_legacy_CI <- all_legacy_nest %>% 
  dplyr::mutate(statistic = purrr::map(.x = booted_ci, # The list-column containing <S3 bootci> objects
                                         ~ .x$t0), # The point estimate
                  lower_ci = purrr::map(.x = booted_ci,
                                        ~ .x$bca[[4]]), # The value of the lower 2.5% limit
                  upper_ci = purrr::map(.x = booted_ci,
                                        ~ .x$bca[[5]])) %>% # The value of teh upper 97.5% limit
    # Drop the list-columns (no longer needed)
    dplyr::select(-data, -booted, -booted_ci) %>%
    # Unnest the dataframe
    tidyr::unnest()

# Join to mean values
all_legacy %<>% inner_join(all_legacy_CI, by="ypd")

g <- all_legacy %>% ggplot(aes(x = ypd, y = mean)) + 
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci), alpha=.5) + 
  geom_line() + 
  geom_point(size=3) + 
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'black') + 
  geom_line(data = (all_legacy %>% mutate(ac = cumsum(mean))), aes(y = ac, x = ypd), lty = 2) +
  theme(panel.grid = element_blank(), 
        strip.background = element_blank(), 
        legend.position = "none") + 
  scale_x_continuous("Years post drougth event", breaks=c(1:6)) + 
  scale_y_continuous("Observed - Predicted Growth", breaks=seq(-0.2, 0.2, by=0.05))
g

# dashed line indicates integrated legacy effects (sensu Anderegg et al. 2015; i.e: sum of legacy effects)

# Integrated legacy effects (sensu Anderegg et al. 2015)
sum(all_legacy$mean)
```

## Legacy effects for site

@@

p1 <- mlegacy %>% ggplot(aes(x = ypd, y = mean)) + 
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill=site), alpha=.5) + 
  geom_line(aes(colour=site)) + 
  geom_point(aes(colour=site), size=3) + 
  geom_line(data = l2005, aes(x = ypd, y =  lag)) + 
  geom_line(data = l2012, aes(x = ypd, y =  lag), linetype = "dashed") + 
  geom_line(data = (mlegacy %>% group_by(site) %>% mutate(ac = cumsum(mean))), 
            aes(y = ac, x = ypd, colour = site), lty = "dotdash") + 
  facet_wrap(~site, labeller = as_labeller(label_site)) + 
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'black') + 
  theme(panel.grid = element_blank(), 
        strip.background = element_blank(), 
        legend.position = "none") + 
  scale_x_continuous("Years post drougth event", breaks=c(1:6)) + 
  scale_y_continuous("Observed - Predicted Growth", breaks=seq(-0.4, 0.2, by=0.05))
